---
title: "Formative Assessment 7"
author: "Vera Aguila"
date: "2024-02-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
In Example 16.3 with 𝜆 = 4 per minute, use R to obtain:
<br>(a) P(T ≤ 0.25) = P(time between submissions is at most 15 seconds);

```{r q1.1}
average_occurence = 4
k <- pexp(0.25, average_occurence)
k
```

<br><br>(b) P(T > 0.5) = P(time between submissions is greater than 30 seconds);
```{r q1.2}
average_occurence = 4
k <- 1-pexp(0.5, average_occurence)
k
```

<br><br>(c) P(0.25 < T < 1) = P(time between submissions is between 15 seconds
and 1 minute).
```{r q1.3}
average_occurence = 4
k <- pexp(1, average_occurence)-pexp(0.25, average_occurence)
k
```

<br><br>
## Question 3
The average rate of job submissions in a computer center is 2 per minute. If
it can be assumed that the number of submissions per minute has a Poisson
distribution, calculate the probability that:
<br>(a) more than two jobs will arrive in a minute;
```{r q3.1}
average_occurence <- 2
x <- 0:2
prob_morethan_2 <- 1 - sum(dpois(x, average_occurence))
cat("Probability of more than two jobs arriving in a minute:", prob_morethan_2)
```
<br><br>(b) at least 30 seconds will elapse between any two jobs;
<br>P(T ≥ 0.5)= P(time between submissions is at least 30 seconds)
```{r q3.2}
k <- 1 - pexp(30/60, average_occurence)
k
```
<br><br>(c) less than 30 seconds will elapse between jobs;
<br>P(T < 0.5)= P(time between submissions is less than 30 seconds)
```{r q3.3}
k <- pexp(30/60, average_occurence)
k
```
<br><br>(d) a job will arrive in the next 30 seconds, if no jobs have arrived in the last
30 seconds.
<br>P(0.5 ≤ T ≤ 1)= P(time between submissions is in between of 30 and 60 seconds)

```{r q3.4}
k <- pexp(60/60, average_occurence) - pexp(30/60, average_occurence)
k
```
<br><br>

## Question 7
A website receives an average of 15 visits per hour, which arrive following a
Poisson distribution.
<br>(a) Calculate the probability that at least 10 minutes will elapse without a
visit.
<br> 10 minutes is 0.16666667 of an hour 
<br>P(0.16666667 ≤ T )= P(time between visits is at least 10 minutes)
```{r q7.1}
average_occurence = 15
k <- pexp(0.16666667, average_occurence)
k
```
<br><br>(b) What is the probability that in any hour, there will be less than eight visits?
<br>P(X < 8 )= P(less than eight visits)

```{r q7.2}
k <- ppois(7, average_occurence)
k
```
<br><br>(c) Suppose that 15 minutes have elapsed since the last visit, what is the probability that a visit will occur in the next 15 minutes.
<br>P(0.25 < T ≤ 0.5)= P(time between visits is between 15 and 30 minutes)
```{r q7.3}
k <- pexp(0.5, average_occurence) - pexp(0.25, average_occurence)
k
```
<br><br>(d) Calculate the top quartile, and explain what it means
```{r q7.4}
k <- qpois(0.75, average_occurence)
k
```

